---
title: "p8105_hw1_yw4660"
output: html_document
---
#### Problem 1
```{r, echo=FALSE}
# import necessary package
# install.packages("moderndive")
library("moderndive")
library("tidyverse")
data("early_january_weather") #load the data
skimr::skim(early_january_weather) #view the data
```
<!--A short description using inline R code-->
The dataset early_january_weather contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.  
The mean temperature is `r mean(early_january_weather$temp, na.rm = TRUE)`.

```{r, echo=FALSE}
# scatterplot
ggplot(early_january_weather,
       aes(x = time_hour, y = temp, color = humid)) +
  geom_point(alpha = 0.6) +
  labs(
    title = "Temperature vs. Time",
    x = "Time",
    y = "Temperature (°F)",
    color = "Humidity"
  ) 
# save it
ggsave("weather_scatterplot.png")
```
<!--A short description of plot-->
The scatterplot shows that temperatures generally increase through the first half of January, rising from around the low 30 °F range to the mid-40s and occasionally near 50 °F. Daily readings vary several degrees, and points with lighter blue coloring—indicating higher humidity—tend to cluster during the warmer mid-month period, suggesting more humid air when it’s warmer.

#### Problem 2

```{r}



```

